Modelling BCG vaccination in the UK

### 2019-04-30 index/06-tb-bcg-improv-outcomes.Rmd
updated wordcount

```{r setup, include = FALSE, eval = TRUE}
## Word count: 3813
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

>>>>

```{r setup, include = FALSE, eval = TRUE}
## Word count: 3869
## Packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(pander)
library(prettypublisher)

### 2019-04-30 index/08-model-development.Rmd
updated wordcount

## Wordcount: 12120
##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")
```

>>>>

## Wordcount: 10220
##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model-development")
```

### 2019-04-30 index/09-model-fitting.Rmd
fixed thesis building in correct format (without packrat
wording tweaks
updated wordcount

##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_fitting")
```

@@

* Mixing rate between UK born and non-UK born ($M$).
* Effective contact rate ($c_{eff}$).
* Historic effective contact rate ($c^{hist}_{eff}$).
* Half life of the effective contact rate ($c^{hist}_{half}$).
* Scale up of time to treatment ($\nu_{scale}$).
* Systematic reporting error ($E_{syst}$).
* Reporting noise ($E_{noise}$).

@@

* Method strengths and weaknesses
* Software strenghts and weaknesses

>>>>

## Wordcount: 5501
##packages
library(tidyverse)
library(ModelTBBCGEngland)
library(kableExtra)
library(pander)
## Resources path
resources_path <- file.path("chapters", "model_fitting")
```

@@

* Mixing rate between UK born and non-UK born ($M$).
* Effective contact rate ($c_{eff}$).
* Historic effective contact rate ($c^{hist}_{eff}$).
* Half life of the effective contact rate ($c^{hist}_{half}$).
* Systematic reporting error ($E_{syst}$).
* Reporting noise ($E_{noise}$).

@@

* Method strengths and weaknesses
* Software strengths and weaknesses

### 2019-04-30 index/index.Rmd
fixed thesis building in correct format (without packrat
updated wordcount

---
author: 'Samuel Abbott'
date: 'April 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "26,067"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---

@@

<!--
If you receive a duplicate label error after knitting, make sure to delete the thesis.Rmd file and then knit again.
-->

>>>>

---
author: 'Samuel Abbott'
date: 'April 2019'
division: 'Bristol Medical School: Population Health Sciences'
advisor: 'Ellen Brooks Pollock'
altadvisor: 'Hannah Christensen'
department: 'Faculty of Health Sciences'
title: 'Modelling BCG vaccination in the UK'
subtitle: 'What is the impact of changing policy?'
wordcount: "36, 969"
knit: bookdown::render_book
site: bookdown::bookdown_site
always_allow_html: yes
output: 
  thesisdown::thesis_pdf: default
  #thesisdown::thesis_gitbook: default
  #thesisdown::thesis_word: default
  #thesisdown::thesis_epub: default
abstract: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = ' ')`
acknowledgements: >
 `r if(knitr:::is_latex_output()) paste(readLines("00-acknowledgements.Rmd"), collapse = ' ')`
declaration: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-declaration.Rmd"), collapse = ' ')`
contribution: >
  `r if(knitr:::is_latex_output()) paste(readLines("00-contribution.Rmd"), collapse = ' ')`
bibliography: bib/thesis.bib
#Download your specific bibliography database file and refer to it in the line above.
csl: csl/bmj.csl
#Download your specific csl file and refer to it in the line above.
lot: true
lof: true
space_between_paragraphs: true
#Delete the # at the beginning of the previous line if you'd like
#to have a blank new line between each paragraph
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
---

@@

<!--
If you receive a duplicate label error after knitting, make sure to delete the thesis.Rmd file and then knit again.
-->
```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
